Paper TITLE

### 2016-08-04 code/Paper.Rmd
Add plot for poverty groups over time

>>>>

```{r, echo = FALSE}
counts <- clean_years %>% 
  # Group and summarise the amount of people in each poverty group each year
  group_by(fmtincrelpovcat, year) %>%
  summarise(count = n()) %>%
  # Clean NAs
  na.omit() %>%
  # Group again by year to calculate relative percentages per year
  group_by(year) %>% 
  mutate(percent = count / sum(count),  
         # Clean the labels
         fmtincrelpovcat = factor(fmtincrelpovcat, 
                                  levels = c("1 LTE Poverty", 
                                             "2 100-150% Poverty", 
                                             "3 150-200% Poverty", 
                                             "4 200%+ Poverty"),  
                                  labels = c("Less than poverty income",   
                                             "100-150% of poverty income",   
                                             "150-200% of poverty income",    
                                             "> 200% of poverty income"),
                                  ordered = T))

ggplot(counts, aes(x = year, 
                   y = percent,
                   fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.5) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdBu", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Precent of households",
       fill = "Household income
relative to poverty income") 
```
